THESIS PROJECT PROPOSAL

### 2019-11-07 project_ashish/paper.tex
commit

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of Standard model the Higgs boson in proton collisions.}
   \label{figure 2}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of Standard model Higgs boson in proton collisions.}
   \label{figure 2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
   \label{figure 7}
\end{figure}
